---
title: |
  Hacking for Social Sciences
subtitle: "Class Is Open. C'mon in."
author: "@whatsgoodio"
institute: "KOF, ETH Zurich"
date: "2020-10-01"
output:
  xaringan::moon_reader:
    css: ["robot-fonts","more.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
      beforeInit: "https://platform.twitter.com/widgets.js"
---

class: center,middle

## live demo: </br> markdown, github, swissdata

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 


---

class: center,middle

## [Background Survey](https://h4sci.shinyapps.io/intro-survey/)

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 


---

class: center,middle

## Overall Course Outline

---

## Schedule

01.10.	10-13	The Big Picture
02.10.	10-14	Git & Workflows

22.10.	10-13	R Programming Crash Course
23.10.	10-14	Programming with Data

19.11.	10-13	Infrastructure
20.11.	10-14	Infrastructure

03.12.	10-13	Semester Projects
04.12.	10-14	Semester Projects

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 


---

## Course Resources

**Read Online**

- [h4sci Slides](https://h4sci.github.io/h4sci-course)
- [h4sci free Online Book](https://h4sci.github.io/h4sci-book)
- [Tasks & Exercises](https://github.com/h4sci/h4sci-tasks)

**Source**

- [Slides: https://github.com/h4sci/h4sci-course](https://github.com/h4sci/h4sci-course)
- [Book: https://github.com/h4sci/h4sci-book](https://github.com/h4sci/h4sci-book)

**Community**
- [R Studio Server](https://teaching.kof.ethz.ch/auth-sign-in) (only available to enrolled ETH students during semester) 
- [Slack Workspace](https://h4sci.slack.com/) (invite only) 
- Zoom Live Sessions (only available to ETH students)

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 



---

class: center,middle

## Course Objectives

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 


---

class: center,middle

## 1. Evaluate the Role of Components in the Tech Stack

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 

---

class: center,middle

## 2. Carpentry Level Version Control + Dev Workflows


<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 

---

class: center,middle

## 3. Applied Data Handling /w Programming Language

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 


---

class: center,middle

## Benchmark: Create a Production Pipeline

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 


---

class: center,middle

## Survey Results

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(ggplot2)
library(data.table)
library(RPostgres)
library(quanteda)

preprocess <- function(df, pattern){
  pattern_id <- paste0("id|group|",pattern)
  subs <- df[,grepl(pattern_id, names(df))]
  names(subs) <- gsub(pattern,"",names(subs))
  dt <- as.data.table(subs)
  m <- melt(dt, id.vars = c("id","cgroup"))
  m
}

fcon <- file("../intro-survey/.pgpass","r")
    con <-  dbConnect(drv = Postgres(), dbname = "postgres", user = "postgres",
                       host = "34.65.173.162",
                      password = readLines(fcon, warn = FALSE))
o <- dbExecute(con,"SET SEARCH_PATH=h4sci")

res <- dbGetQuery(con,"SELECT * FROM responses")

dbDisconnect(con)

```



---

## Survey Results: General

```{r, echo=FALSE}

words <- gsub(" vs. |,,", ",",paste(res$general,collapse = ","))

quanteda::textplot_wordcloud(dfm(words,remove = ","),
                             color = rev(viridis::viridis_pal()(6)),
                             min_count = 1)


```

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 


---


## Survey Results: Languages

```{r, echo=FALSE, fig.width=14}

lang <- preprocess(res, "l_")
gg_lang <- ggplot(data = lang)
gg_lang +
  geom_bar(aes(x = as.factor(value), fill = variable)) +
  facet_wrap("variable", nrow = 2) + 
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.spacing = unit(4, "lines"),
        text = element_text(size=15)) +
  scale_x_discrete(name ="Language",
                   limits=factor(1:5)) +
  scale_fill_viridis_d()



```


<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 



---


## Survey Results: Workflow

```{r, echo=FALSE, fig.width=14}

wf <- preprocess(res, "w_")
gg_lang <- ggplot(data = wf)
gg_lang +
  geom_bar(aes(x = as.factor(value), fill = variable)) +
  facet_wrap("variable", nrow = 1) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.spacing = unit(4, "lines"),
        text = element_text(size=15)) +
  scale_x_discrete(name ="Language",
                   limits=factor(1:5)) +
  scale_fill_viridis_d()



```

<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 


---


class: center,middle

## Individual Introduction


<div class="my-footer"><span><div class="footer-text" align="right">"Hacking for Social Sciences" by Dr. Matthias Bannert is licensed under <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/?ref=chooser-v1">CC BY-NC-SA 4.0</a></div></span></div> 













