---
title: |
  Hacking for Social Sciences
subtitle: "Programming with Data"
author: "@whatsgoodio"
institute: "KOF, ETH Zurich"
date: "2020-10-23"
output:
  xaringan::moon_reader:
    css: ["robot-fonts","more.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
      beforeInit: "https://platform.twitter.com/widgets.js"
---

class: center,middle

# Data in Social Sciences

---


## Data Generating Processes: Simulation


.pull-left[

### Why ? 

- Analyzing Complex Systems
- Demos
- Proposals / Grants

]


.pull-right[

### Process

```{r}
set.seed(123)
rnorm(3)

set.seed(1)
rnorm(3)

set.seed(123)
rnorm(3)

```



]




---


## Data Generating Processes: Logging / Tracking


.pull-left[

### Process

- webservers,
- mobile phones
- IoT devices
- tracking tools, e.g., Google Analytics

]

.pull-right[

### Form of Resulting Data 

- text files
- granular
- event based
- biased (tracking)

]


---


## Data Generating Processes: Surveys


.pull-left[

### Process

- multi mode surveys (paper / online forms)
- Recordings

]

.pull-right[

### Form of Resulting Data 

- rectangular data (1-line-1-observation)
- text 
- cross sectional 
- longitudinal data


]


---


## Data Generating Processes: APIs, Web Scraping


.pull-left[

### Process

- Automated, regular updates
- Transformation of structured data into analysis friendly datasets

]

.pull-right[

### Form of Resulting Data 

- text strings
- nested data
- standardized data

]






---



class:center,middle

## What DGPs Have You Worked With? 

## What DGPs Do You Expect to Face in Your Work ? 


---


## Types of Datasets: Time Series
  

.pull-left[

```{r, message=FALSE, warning=FALSE, fig.height=4}
library(kofdata)
library(tstools)

tsl <- window(get_time_series("ch.kof.barometer"))
tsplot("KOF Barometer" = 
         window(tsl$ch.kof.barometer,
                start = c(2010,1))
       )

```


]  


.pull-right[

**in memory**

- ts
- xts
- tsibble
- zoo


**on disk**

- .csv (long format, .csv Format)
- .xml
- .json
- .RData


]

<br>
<br>



> (!) Try out the free `tsbox` package to easily switch from one representation 
to another.
  


---


## Types of Datasets: Cross Sectional Data


---


## Types of Datasets: Panel Data
  
  
---
  
## Types of Datasets: Nested Data


---

















